flowCore: data structures package for flow cytometry data

### 2008-04-08 inst/doc/HowTo-flowCore.Rnw
making sure that the samplesare in the same order after splitting. Also added a couple of updates to the documentation
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@30903 bc3139a8-67e5-0310-9ffc-ced21a209358

\section{Introduction}
Traditionally, flow cytometry has been a tube-based technique limited to small-scale laboratory and clinical studies. 
High throughput methods for flow cytometry have recently been developed for drug discovery and advanced research methods 
\citep{Gasparetto2004}. As an example, the flow cytometry high content screening (FC-HCS) can process up 
to a thousand samples daily at a single workstation, and the results have been equivalent or superior to traditional 
manual multiparameter staining and analysis techniques. \\

The amount of information generated by high throughput technologies such as FC-HCS need to be transformed into 
executive summaries (which are brief enough) for creative studies by a human researcher \citep{Brazma2001}. 
Standardization is critical when developing new high throughput technologies and their associated information services 
\citep{Brazma2001, Chicurel2002, Boguski2003}. Standardization efforts have been made in clinical cell analysis 
by flow cytometry \citep{Keeney2004}, however data interpretation has not been standardized for even low throughput FCM. 
It is one of the most difficult and time consuming aspects of the entire analytical process as well as a primary source 
of variation in clinical tests, and investigators have traditionally relied on intuition rather than standardized statistical inference 
\citep{Bagwell2004,Braylan2004,Parks1997,Suni2003}. In the development of standards in high throughput FCM, 
few progress has been done in term of Open Source software. In this article we propose R data structures to handle 
flow cytometry data through the main steps of preprocessing: compensation, transformation, filtering.\\

>>>>

\section{Introduction}
Traditionally, flow cytometry has been a tube-based technique limited
to small-scale laboratory and clinical studies.  High throughput
methods for flow cytometry have recently been developed for drug
discovery and advanced research methods \citep{Gasparetto2004}. As an
example, the flow cytometry high content screening (FC-HCS) can
process up to a thousand samples daily at a single workstation, and
the results have been equivalent or superior to traditional manual
multiparameter staining and analysis techniques.

The amount of information generated by high throughput technologies
such as FC-HCS need to be transformed into executive summaries (which
are brief enough) for creative studies by a human researcher
\citep{Brazma2001}.  Standardization is critical when developing new
high throughput technologies and their associated information services
\citep{Brazma2001, Chicurel2002, Boguski2003}. Standardization efforts
have been made in clinical cell analysis by flow cytometry
\citep{Keeney2004}, however data interpretation has not been
standardized for even low throughput FCM.  It is one of the most
difficult and time consuming aspects of the entire analytical process
as well as a primary source of variation in clinical tests, and
investigators have traditionally relied on intuition rather than
standardized statistical inference
\citep{Bagwell2004,Braylan2004,Parks1997,Suni2003}. In the development
of standards in high throughput FCM, few progress has been done in
term of Open Source software. In this article we propose R data
structures to handle flow cytometry data through the main steps of
preprocessing: compensation, transformation, filtering.
